---
title: "CONISI Codebook"
author: "Prepared by: Roxanne Beauclair (roxanne.beauclair@wimmy.co.za)"
date: 'Last updated on: `r lubridate::today()`'
output:
  prettydoc::html_pretty:
    theme: hpstr
    highlight: vignette
    toc: true
    toc_depth: 2
toc-title: "Table of Contents"
vignette: >
  %\VignetteIndexEntry{CONISI Codebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE, 
  message = FALSE,  
  echo = FALSE
)

# Allow duplicate chunk labels
options(knitr.duplicate.label = "allow")
```

```{r setup, include = FALSE}

library(tidyverse)

# ===================
# Relative file paths
# ===================
#data_file <- system.file("extdata", "Example_Model_Output.RData", package = "conisi")

data_file <- "Example_Model_Output.RData"

# =============
# Load datasets
# =============
load(data_file)
df <- conisi::mutate_model_output(modelOutput,
                          pop = 168559618,
                          report_lag = 2,
                          start = lubridate::ymd("2020-03-12"))


```


# **Metadata**

<br>

**Dataset name**: CONISI Model Output <br>
**Description of dataset**: The dataset you are using will be specific to a region - either South Africa, Peru, Brazil, Chile, Zimbabwe, Limpopo Province, North West Province, Northern Cape Province, or Eastern Cape Province. Moreover, each value will be unique to the point in time for which the model was run. All datasets for each region and model run will have the same number and names of columns. This dataset currently contains `r ncol(df)` variables. Each row in the dataset represents a unique model run and time point in the model run. For example, this dataset of output contains `r nrow(df)` total rows of output, that belong to `r round(nrow(df) / max(df$time))` model runs. Each of those model runs has a unique set of parameters that were used as input. Each model run has a row for `r max(df$time)` time steps.

<br>

# **Description of Variables**

<br>

There are five different types of variables: identifiers, parameters, compartments, compartment combinations, and flows.

<br>

## **Identifiers**

<br>

These variables in combination uniquely identify each row in the dataset.

<br>

### experiment 

<br>

This variable contains an integer that identifies the model run that the row belonged to.

<br>
<br>

### time

<br>

This variable contains an integer that represents the number of days that have passed within the model world.

<br>
<br>

### date

<br>

This is the conversion of the `time` variable into a date in the real world based upon when the local epidemic started and assumed reporting delays. The variable is formatted as YYYY-MM-DD. In this dataset the earliest date simulated is `r format(min(df$date), "%A, %d %B %Y")` and the most recent date availble is `r format(max(df$date), "%A, %d %B %Y")`.

<br>

## **Parameters**

<br>

The parameter variables were used as inputs into the model. They govern the rates at which people in the population move from one compartment (i.e. disease/health state) to another. Each model run (i.e. experiment) uses a unique set of parameters. The parameters are mostly the same across all time steps for that particular model run, but a few of the parameters are time-varying. Parameter variables are prefixed with "par_".

<br>

### par_a_1d 

<br>

This is the infectivity of *diagnosed pre-symptomatic* individuals relative to undiagnosed mildly infected individuals.

<br>

```{r, include = FALSE}
var <- "par_a_1d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_a_1u

<br>

This is the infectivity of *undiagnosed pre-symptomatic* individuals relative to undiagnosed mildly infected individuals.

<br>

```{r, include = FALSE}
var <- "par_a_1u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_a_2d

<br>

This is the infectivity of *diagnosed asymptomatic* individuals relative to undiagnosed mildly infected individuals.

<br>

```{r, include = FALSE}
var <- "par_a_2d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_a_2u

<br>

This is the infectivity of *undiagnosed asymptomatic* individuals relative to undiagnosed mildly infected individuals.

<br>

```{r, include = FALSE}
var <- "par_a_2u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_a_md

<br>

This is the infectivity of *diagnosed mildly infected* individuals relative to undiagnosed mildly infected individuals.

<br>

```{r, include = FALSE}
var <- "par_a_md"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_a_sd

<br>

This is the infectivity of *diagnosed severely infected* individuals relative to undiagnosed mildly infected individuals.

<br>

```{r, include = FALSE}
var <- "par_a_sd"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_a_su

<br>

This is the infectivity of *undiagnosed severely infected* individuals relative to undiagnosed mildly infected individuals.

<br>

```{r, include = FALSE}
var <- "par_a_su"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_b_b

<br>

This is the effective contact rate, which encompasses all of the biological and behavioral considerations that influence contacts between individuals that lead to transmission.

<br>

```{r, include = FALSE}
var <- "par_b_b"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_12u

<br>

This is the rate at which *undiagnosed pre-symptomatic* individuals become undiagnosed and asymptomatic, never to develop symptoms.

<br>

```{r, include = FALSE}
var <- "par_c_12u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_1mu

<br>

This is the rate at which *undiagnosed pre-symptomatic* individuals become undiagnosed with mild infection symptoms.

<br>

```{r, include = FALSE}
var <- "par_c_1mu"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_1su

<br>

This is the rate at which *undiagnosed pre-symptomatic* individuals become undiagnosed with severe infection symptoms.

<br>

```{r, include = FALSE}
var <- "par_c_1su"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_ceil

<br>

This is the maximum number of people who can be in critical care at a single time step. 

<br>

```{r, include = FALSE}
var <- "par_c_ceil"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_e1u

<br>

This is the rate at which *exposed, but not infectious*, individuals become undiagnosed pre-symptomatic infectious individuals.

<br>

```{r, include = FALSE}
var <- "par_c_e1u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_d_1

<br>

This is the rate at which *pre-symptomatic* individuals get diagnosed.

<br>

```{r, include = FALSE}
var <- "par_d_1"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_d_2

<br>

This is the rate at which *truly asymptomatic* individuals get diagnosed.

<br>

```{r, include = FALSE}
var <- "par_d_2"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_d_m

<br>

This is the rate at which *mildly infected* individuals get diagnosed.

<br>

```{r, include = FALSE}
var <- "par_d_m"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_d_s

<br>

This is the rate at which *severely infected* individuals get diagnosed.

<br>

```{r, include = FALSE}
var <- "par_d_s"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_ddf

<br>

This is the fraction of deaths that happened outside of the hospital where COVID-19 is identified as the cause of death. 

<br>

```{r, include = FALSE}
var <- "par_ddf"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_delta_c

<br>

This is the rate at which people in *critical care* die.

<br>

```{r, include = FALSE}
var <- "par_delta_c"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_delta_h

<br>

This is the rate at which people in the *hospital* die before going to critical care.

<br>

```{r, include = FALSE}
var <- "par_delta_h"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_delta_h_adjust

<br>

This is the factor by which you multiply the `delta_h` parameter if you want to decrease the rate at a specific point in time. 

<br>

```{r, include = FALSE}
var <- "par_delta_h_adjust"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_delta_su

<br>

This is the rate at which *undiagnosed, severely infected* people die.

<br>

```{r, include = FALSE}
var <- "par_delta_su"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_eta_u

<br>

This is the rate at which *undiagnosed severely infected* people are hospitalised.

<br>

```{r, include = FALSE}
var <- "par_eta_u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_FOIadjust

<br>

This is the factor by which you multiply the force of infection if you want to decrease the rate at a specific point in time. 

<br>

```{r, include = FALSE}
var <- "par_FOIadjust"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_h_ceil

<br>

The maximum number of people who can be in the hospital at a given time.

<br>

```{r, include = FALSE}
var <- "par_h_ceil"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_hdf

<br>

The fraction of all people who go to the hospital with COVID-19 that are actually diagnosed with COVID-19.

<br>

```{r, include = FALSE}
var <- "par_hdf"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_r_2u

<br>

This is the rate at which *undiagnosed truly asymptomatic infected* individuals recover.

<br>

```{r, include = FALSE}
var <- "par_r_2u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_r_h

<br>

This is the rate at which *hospitalised* individuals recover, without going to critical care.

<br>

```{r, include = FALSE}
var <- "par_r_h"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_r_mu

<br>

This is the rate at which *undiagnosed mildly infected* individuals recover.

<br>

```{r, include = FALSE}
var <- "par_r_mu"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_r_p

<br>

This is the rate at which individuals in the *post-critical care ward* recover.

<br>

```{r, include = FALSE}
var <- "par_r_p"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_rho

<br>

This is the rate that those in the *critical care ward* move to the post-critical care ward.

<br>

```{r, include = FALSE}
var <- "par_rho"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_theta

<br>

This is the rate that those who are *hospitalised* move to the critical care ward.

<br>

```{r, include = FALSE}
var <- "par_theta"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_r_2d

<br>

This is the rate that those who are *diagnosed and asymptomatic* recover.

<br>

```{r, include = FALSE}
var <- "par_r_2d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_r_md

<br>

This is the rate that those who are *diagnosed and mildly infected* recover.

<br>

```{r, include = FALSE}
var <- "par_r_md"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_12d

<br>

This is the rate that those who are *diagnosed and pre-symptomatic* become a truly asymptomatic infected individual.

<br>

```{r, include = FALSE}
var <- "par_c_12d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_1md

<br>

This is the rate that those who are *diagnosed and pre-symptomatic* become a mildly infected individual.

<br>

```{r, include = FALSE}
var <- "par_c_1md"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_c_1sd

<br>

This is the rate that those who are *diagnosed and pre-symptomatic* become a severely infected individual.

<br>

```{r, include = FALSE}
var <- "par_c_1sd"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_eta_d

<br>

This is the rate that those who are *diagnosed and severely infected* become hosptialised.

<br>

```{r, include = FALSE}
var <- "par_eta_d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_delta_sd

<br>

This is the rate that those who are *diagnosed and severely infected* die without ever going to the hospital.

<br>

```{r, include = FALSE}
var <- "par_delta_sd"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### par_d_e

<br>

This is the rate that *undiagnosed exposed, but not infectious* individuals become diagnosed.

<br>

```{r, include = FALSE}
var <- "par_d_e"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

## **Compartments**

<br>

These variables refer to the number of people who are in a specific disease state at a given point in time.

<br>

### S

<br>

This is the total number of people who are *susceptible to infection* at a specific time step.

<br>

```{r, include = FALSE}
var <- "S"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### E_d

<br>

This is the total number of people who are *diagnosed with COVID-19, but not infectious yet* at a specific time step.

<br>

```{r, include = FALSE}
var <- "E_d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### E_u

<br>

This is the total number of people who are *undiagnosed and infected* with COVID-19, but not infectious yet at a specific time step.

<br>

```{r, include = FALSE}
var <- "E_u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_1d

<br>

This is the total number of people who are *diagnosed and pre-symptomatic* at a specific time step.

<br>

```{r, include = FALSE}
var <- "I_1d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_1u

<br>

This is the total number of people who are *undiagnosed and pre-symptomatic* at a specific time step.

<br>

```{r, include = FALSE}
var <- "I_1u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_2d

<br>

This is the total number of people who are *diagnosed and asymptomatic* at a specific time step.

<br>

```{r, include = FALSE}
var <- "I_2d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_2u

<br>

This is the total number of people who are *undiagnosed and asymptomatic* at a specific time step.

<br>

```{r, include = FALSE}
var <- "I_2u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_md

<br>

This is the total number of people who are *diagnosed and mildly infected* at a specific time step.

<br>

```{r, include = FALSE}
var <- "I_md"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_mu

<br>

This is the total number of people who are *undiagnosed and mildly infected* at a specific time step.

<br>

```{r, include = FALSE}
var <- "I_mu"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_sd

```{r, include = FALSE}
var <- "I_sd"
```

<br>

This is the total number of people who are *diagnosed and severely infected* at a specific time step. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### I_su

<br>

This is the total number of people who are *undiagnosed and severely infected* at a specific time step.

<br>

```{r, include = FALSE}
var <- "I_su"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### R_2d

<br>

This is the total number of *diagnosed asymptomatic* people who had recovered by a specific time step.

<br>

```{r, include = FALSE}
var <- "R_2d"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

<br>

### R_2u

<br>

This is the total number of *undiagnosed asymptomatic* people who had recovered by a specific time step.

<br>

```{r, include = FALSE}
var <- "R_2u"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### R_md

<br>

This is the total number of *diagnosed mildly infected* people who had recovered by a specific time step.

<br>

```{r, include = FALSE}
var <- "R_md"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### R_mu

<br>

This is the total number of *undiagnosed mildly infected* people who had recovered by a specific time step.

<br>

```{r, include = FALSE}
var <- "R_mu"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### H

<br>

This is the total number of people who are *hospitalised*, but not in critical care, at a specific time step.

<br>

```{r, include = FALSE}
var <- "H"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### R_h

<br>

This is the total number of *hospitalised* people who had recovered by a specific time step.

<br>

```{r, include = FALSE}
var <- "R_h"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### C

```{r, include = FALSE}
var <- "C"
```

<br>

This is the total number of people in *critical care* at a specific time step. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### P

<br>

This is the total number of people who are *post-critical care* at a specific time step.

<br>

```{r, include = FALSE}
var <- "P"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### R_c

<br>

This is the total number of people who were *in critical care* who had recovered by a specific time step.

<br>

```{r, include = FALSE}
var <- "R_c"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### D_s

<br>

This is the total number of *severely infected, but not hospitalised* individuals that had died by a specific time step.

<br>

```{r, include = FALSE}
var <- "D_s"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### D_h

<br>

This is the total number of *hospitalised* individuals that had died by a specific time step.

<br>

```{r, include = FALSE}
var <- "D_h"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### D_c

<br>

This is the total number of individuals who were in *critical care* that had died by a specific time step.

<br>

```{r, include = FALSE}
var <- "D_c"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

## **Flows**

<br>

These are variables produced by the model that represent the cumulative number of people who were in a given disease state by a specific point in time. 

<br>

### ConfirmedCases

```{r, include = FALSE}
var <- "ConfirmedCases"
```

<br>

This is the cumulative number of cases that have been diagnosed by a specific time. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### ContribAll

<br>

This is the cumulative number of all people - diagnosed and undiagnosed - who have ever been infected by a specific time.

<br>

```{r, include = FALSE}
var <- "ContribAll"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### ContribNonSympt

<br>

This is the cumulative cases caused by asymptomatic infections at a specific time.

<br>

```{r, include = FALSE}
var <- "ContribNonSympt"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### eta_d_cumul_flow

<br>

This is the cumulative number of hospitalizations, among diagnosed cases, by a specific time.

<br>

```{r, include = FALSE}
var <- "eta_d_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### eta_u_cumul_flow

<br>

This is the cumulative number of hospitalizations, among undiagnosed infections, by a specific time.

<br>

```{r, include = FALSE}
var <- "eta_u_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### r_h_cumul_flow

<br>

This is the cumulative number of recoveries, among those in hospital (not critical care), by a specific time.

<br>

```{r, include = FALSE}
var <- "r_h_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### theta_cumul_flow

<br>

This is the cumulative of hospitalised cases that have gone to critical care, by a specific time.

<br>

```{r, include = FALSE}
var <- "theta_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Asymp_diagnozed_cumul_flow

<br>

This is the cumulative number of diagnoses among asymptomatic cases, by a specific time.

<br>

```{r, include = FALSE}
var <- "Asymp_diagnozed_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Symp_diagnozed_cumul_flow

<br>

This is the cumulative number of diagnoses among symptomatic cases, by a specific time.

<br>

```{r, include = FALSE}
var <- "Symp_diagnozed_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Asymp_inf_cumul_flow

<br>

This is the cumulative number of pre-symptomatic infections that became asymptomatic by a specific time.

<br>

```{r, include = FALSE}
var <- "Asymp_inf_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Symp_inf_cumul_flow

<br>

This is the cumulative number of pre-symptomatic infections that became symptomatic by a specific time.

<br>

```{r, include = FALSE}
var <- "Symp_inf_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

## **Combinations**

<br>

These variables that were created from different combinations of the compartmental, flow, and parameter variables. 

<br>

### R0

<br>

This is the basic reproduction number. It is the average number of secondary infections produced by one case in a population where everyone is still susceptible.

<br>

```{r, include = FALSE}
var <- "R0"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Reff

<br>

This is the effective reproductive number. It is the average number of secondary infections produced by one case in a population where some people are susceptible and others are not susceptible because they have been vaccinated or infected.

<br>

```{r, include = FALSE}
var <- "Reff"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### AllInfections

<br>

This is the total number of people who are exposed or infected, whether diagnosed or undiagnosed, at single point in time.

<br>

```{r, include = FALSE}
var <- "AllInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### ActiveInfections

```{r, include = FALSE}
var <- "ActiveInfections"
```

<br>

This is the total number of people at a single point in time who are infected, whether diagnosed or undiagnosed, who we assume are actively transmitting infection. It excludes those who are exposed, but not yet infectious, as well as those who are hospitalised or in critical care. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### SymptKnownAsymptInfections

<br>

This is the total number of people at a single point in time who symptomatic infections, whether diagnosed or undiagnosed, as well as diagnosed asymptomatic infections. It excludes those who are hospitalised or in critical care.

<br>

```{r, include = FALSE}
var <- "SymptKnownAsymptInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### SymptKnownInfections


```{r, include = FALSE}
var <- "SymptKnownInfections"
```

<br>

This is the total number of people at a single point in time who have a diagnosed symptomatic infection (mild or severe). It excludes those who are hospitalised or in critical care. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### SymptUnknownInfections

<br>

This is the total number of people at a single point in time who have a undiagnosed symptomatic infection (mild or severe). It excludes those who are hospitalised or in critical care.

<br>

```{r, include = FALSE}
var <- "SymptUnknownInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### AsymptKnownInfections

<br>

This is the total number of people at a single point in time who have a diagnosed asymptomatic infection. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, include = FALSE}
var <- "AsymptKnownInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### AsymptUnknownInfections

<br>

This is the total number of people at a single point in time who have an undiagnosed asymptomatic infection.

<br>

```{r, include = FALSE}
var <- "AsymptUnknownInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### SymptInfections

```{r, include = FALSE}
var <- "SymptInfections"
```

<br>

This is the total number of people at a single point in time who have a symptomatic infection (diagnosed and undiagnosed), but not hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### AsymptInfections

```{r, include = FALSE}
var <- "AsymptInfections"
```

<br>

This is the total number of people at a single point in time who have an asymptomatic infection (diagnosed and undiagnosed). In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### KnownInfections

```{r, include = FALSE}
var <- "KnownInfections"
```

<br>

This is the total number of people at a single point in time who have a diagnosed infection (not including hospitalised patients). In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### UnknownInfections

<br>

This is the total number of people at a single point in time who have an undiagnosed infection.

<br>

```{r, include = FALSE}
var <- "UnknownInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### SevereKnownMildInfections

<br>

This is the total number of people at a single point in time who have a severe infection (diagnosed and undiagnosed), or a diagnosed mild infection (not including hospitalised patients).

<br>

```{r, include = FALSE}
var <- "SevereKnownMildInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### SevereInfections

```{r, include = FALSE}
var <- "SevereInfections"
```

<br>

This is the total number of people at a single point in time who have a severe infection (diagnosed and undiagnosed), but not including hospitalised patients. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hospitalizations

```{r, include = FALSE}
var <- "Hospitalizations"
```

<br>

This is the total number of people at a single point in time who are hospitalised. It includes those in normal, critical care, and post-critical care units. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hosp_I_sd

```{r, include = FALSE}
var <- "Hosp_I_sd"
```

<br>

This is the total number of people at a single point in time who have a severe diagnosed infection or are hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hosp_SevereInfections

```{r, include = FALSE}
var <- "Hosp_SevereInfections"
```

<br>

This is the total number of people at a single point in time who have a severe infection (diagnosed or undiagnosed) or are hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hosp_SevereKnownMildInfections

```{r, include = FALSE}
var <- "Hosp_SevereKnownMildInfections"
```

<br>

This is the total number of people at a single point in time who have a diagnosed mild infection, severe infection (diagnosed or undiagnosed) or are hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hosp_SymptInfections

```{r, include = FALSE}
var <- "Hosp_SymptInfections"
```

<br>

This is the total number of people at a single point in time who have a symptomatic infection (diagnosed or undiagnosed) or are hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.


<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hosp_SymptKnownAsymptInfections

```{r, include = FALSE}
var <- "Hosp_SymptKnownAsymptInfections"
```

<br>

This is the total number of people at a single point in time who have a diagnosed asymptomatic infection, symptomatic infection (diagnosed or undiagnosed), or are hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hosp_ActiveInfections

```{r, include = FALSE}
var <- "Hosp_ActiveInfections"
```

<br>

This is the total number of people at a single point in time who have an active infection or are hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Hosp_SymptKnownInfections

```{r, include = FALSE}
var <- "Hosp_SymptKnownInfections"
```


<br>

This is the total number of people at a single point in time who a diagnosed symptomatic infection (mild or severe) or are hospitalised. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### hosp_nonicu

```{r, include = FALSE}
var <- "hosp_nonicu"
```

<br>

This is the total number of cases at a single point in time who are in any non-critical care ward. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### deaths_hosp

```{r, include = FALSE}
var <- "deaths_hosp"
```

<br>

This is the total number of deaths among people who were hospitalised in a normal ward or critical care unit. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### NotWorking

```{r, include = FALSE}
var <- "NotWorking"
```

<br>

This is the total number of people at a single point in time who have a diagnosed infection (pre-symptomatic, asymptomatic, mild or severe) or are hospitalised. Theoretically, these people would not be at work at this point in time. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### ReturnWork_cumul_flow 

<br>

This is the total number of people who have recovered from an infection by a specific point in time.

<br>

```{r, include = FALSE}
var <- "ReturnWork_cumul_flow"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### AllDeaths

```{r, include = FALSE}
var <- "AllDeaths"
```

<br>

This is the total number of people who have died by a specific point in time. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Prevalence

```{r, include = FALSE}
var <- "Prevalence"
```

<br>

This is the fraction of the population who has an active infection at a single point in time, not including hospitalised patients. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Exposure

```{r, include = FALSE}
var <- "Exposure"
```

<br>

This is the fraction of the population who has been exposed or infected by a specific point in time. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### FracSymptKnown

<br>

This is the fraction of active infections (not hospitalised) at a single point in time, which are symptomatic and diagnosed.

<br>

```{r, include = FALSE}
var <- "FracSymptKnown"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### FracSymptUnknown

<br>

This is the fraction of active infections (not hospitalised) at a single point in time, which are symptomatic and undiagnosed.

<br>

```{r, include = FALSE}
var <- "FracSymptUnknown"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### FracAsymptKnown

<br>

This is the fraction of active infections (not hospitalised) at a single point in time, which are asymptomatic and diagnosed.

<br>

```{r, include = FALSE}
var <- "FracAsymptKnown"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### FracAsymptUnknown

<br>

This is the fraction of active infections (not hospitalised) at a single point in time, which are asymptomatic and undiagnosed.

<br>

```{r, include = FALSE}
var <- "FracAsymptUnknown"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### FracHospSymptKnown

<br>

This is the fraction of hospitalised or symptomatic infections at a single point in time, which are diagnosed.

<br>

```{r, include = FALSE}
var <- "FracHospSymptKnown"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### FracAsymptKnown2

<br>

This is the fraction of asymptomatic infections at a single point in time, which are diagnosed.

<br>

```{r, include = FALSE}
var <- "FracAsymptKnown2"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### idf

<br>

This is the fraction of all infections at a single point in time, which are diagnosed.

<br>

```{r, include = FALSE}
var <- "idf"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### ifr

<br>

This is the fraction of all people who have been infected, which have died by a point in time.

<br>

```{r, include = FALSE}
var <- "ifr"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### cfr

<br>

This is the fraction of all diagnosed infections, which have died by a point in time.

<br>

```{r, include = FALSE}
var <- "cfr"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### AllDailyInfections

<br>

This is the number of new infections that take place each day. It includes diagnosed, undiagnosed, asymptomatic, symptomatic.

<br>

```{r, include = FALSE}
var <- "AllDailyInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### NonSymptDailyInfections

<br>

This is the number of new infections caused by asymptomatic cases. It includes diagnosed and undiagnosed infections.

<br>

```{r, include = FALSE}
var <- "NonSymptDailyInfections"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### RelContribNonSympt

<br>

This is the fraction of all new cases each day, which are caused by asymptomatic infections.

<br>

```{r, include = FALSE}
var <- "RelContribNonSympt"
```

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### NewCases

```{r, include = FALSE}
var <- "NewCases"
```

<br>

This is the number of new diagnosed infections each day. It includes asymptomatic and symptomatic infections. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### NewDeaths

```{r, include = FALSE}
var <- "NewDeaths"
```

<br>

This is the number of new deaths each day. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.


<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### eta_d_flow

```{r, include = FALSE}
var <- "eta_d_flow"
```

<br>

This is the number of new hospitalisations each day that occur from diagnosed cases. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### eta_u_flow

```{r, include = FALSE}
var <- "eta_u_flow"
```

<br>

This is the number of new hospitalisations each day that occur from undiagnosed infections. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### r_h_flow

```{r, include = FALSE}
var <- "r_h_flow"
```

<br>

This is the number of new recoveries each day that occur from hospitalised (not critical care) cases. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### delta_h_flow


```{r, include = FALSE}
var <- "delta_h_flow"
```

<br>

This is the number of new deaths each day that occur from hospitalised (not critical care) cases. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### theta_flow 

```{r, include = FALSE}
var <- "theta_flow"
```

<br>

This is the number of new patients that enter critical care each day. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Symp_diagnozed_flow

```{r, include = FALSE}
var <- "Symp_diagnozed_flow"
```

<br>

This is the number of newly diagnosed symptomatic infections that occur each day. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.


<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### Asymp_diagnozed_flow

```{r, include = FALSE}
var <- "Asymp_diagnozed_flow"
```

<br>

This is the number of newly diagnosed asymptomatic infections that occur each day. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>


```{r, child = "Numeric_Description_Template.Rmd"}

```

<br>

### ReturnWork_flow

```{r, include = FALSE}
var <- "ReturnWork_flow"
```

<br>

This is the number of employees (newly recovered cases) that return to work each day. In this dataset there are also `r paste0(var, "_mean")`, `r paste0(var, "_min")`, and `r paste0(var, "_max")` variables. These have the same definition, except they represent the mean, min and max values across all experiments at a given time point.

<br>

```{r, child = "Numeric_Description_Template.Rmd"}

```




